\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-09 docs/paper/paper.tex
More on experimental validation.

\subsection{Experimental validation}
% Section on how we plan on demonstrating the empirical value of research.
% Full description from step 1 to final data set
Our analysis consisted of two parts, corresponding to the structural and directional parts of PC algorithm.
Firstly we discerned structure by using brain resting-state time series fMRI data with structure PC.
The generated structure is the same for all variants of PC discussed and proposed, as only the first separating set is used in finding unshielded triples.
We compared the generated structure with a Bayesian inference approach on finding structural connectivity from diffusion weighted imaging.
Comparison between structures is done visually with an expert on brain anatomy.
To increase the stability of found structures within subjects, we apply stability selection for different node permutations by Meinshausen and B{\"u}hlmann \cite{meinshausen2010}.

The second part of our analysis is about discerning orientation within the found structure.
We applied the directionality rules of original PC, modified PC and EMS-PC.

\subsection{Data acquisition}
% TODO: vraag Max naar de details van de meetmethode en subject acquisition
The above analysis was conducted on the same dataset as in \cite{hinne2013structfunc}. %TODO check citation.
The dataset consists of fMRI

We will apply the mentioned methods on structural and functional data gathered from human subjects.
For this we are largely dependent on data collected by others.
Hinne et al. has provided fMRI time-series data and structural network data as used and derived in \cite{hinne2013}, of which six subjects were selected at random.
We can estimate functional connectivity from fMRI-measurement in combination with structural 
networks according to a procedure by Hinne et al. \cite{hinne2013structfunc}.
To find effective connectivity, both structural networks and functional data is needed.

>>>>

\subsection{Experimental validation}
% Section on how we plan on demonstrating the empirical value of research.
% Full description from step 1 to final data set
Our analysis consisted of two parts, corresponding to the structural and directional parts of PC algorithm.
Firstly we discerned structure by using brain resting-state time series fMRI data with structure PC.
The generated structure is the same for all variants of PC discussed and proposed, as only the first separating set is used in finding unshielded triples.
We compared the generated structure with a Bayesian inference approach on finding structural connectivity from diffusion weighted imaging.
Comparison between structures is done visually with an expert on brain anatomy.
To increase the stability of found structures within subjects, we apply stability selection for different node permutations by Meinshausen and B{\"u}hlmann \cite{meinshausen2010}.
Multi-subject comparison was done by averaging and inspecting standard deviation over subjects.

The second part of our analysis is about discerning orientation within the found structure.
We applied the directionality rules of original PC, modified PC and EMS-PC as mentioned above.
Resulting connectivity patterns are visually compared by an expert for anatomical correctness.
To compare between methods, we compare the consistency of methods to mark a specific connection as directional over permutations.
Of specific interest here are non-symmetrical orientations.
We again applied stability selection for a sufficiently large number of permutations per subject.

\subsection{Data acquisition}
% TODO: vraag Max naar de details van de meetmethode en subject acquisition
The above analysis was conducted on the same dataset as in \cite{hinne2013structfunc}. %TODO check citation.
We will apply the mentioned methods on structural and functional data gathered from human subjects.
For this we are largely dependent on data collected by others.
Hinne et al. has provided fMRI time-series data and structural network data as used and derived in \cite{hinne2013}, of which six subjects were selected at random.
We can estimate functional connectivity from fMRI-measurement in combination with structural 
networks according to a procedure by Hinne et al. \cite{hinne2013structfunc}.
To find effective connectivity, both structural networks and functional data is needed.
